# True Parametric Models


```{r, warning=FALSE,message=FALSE,echo=FALSE}
set.seed(1234)

```


```{r, warning=FALSE,message=FALSE,echo=FALSE}
# Load packages (install manually before running if not present)
# To install: install.packages(c("data.table", "ggplot2", "truncnorm", "mvtnorm", "nimble"))
library(data.table)
library(ggplot2)
library(truncnorm)
library(mvtnorm)
library(nimble, warn.conflicts = FALSE)

# Enable Nimble options for saving intermediates and verbose output
nimbleOptions(saveIntermediates = TRUE)  # Saves generated C++ code files
nimbleOptions(verbose = TRUE)           # Provides detailed compilation output


digCom_data <- read.csv("non-comp_dataset.csv")
digCom_df = data.frame(digCom_data)
head(digCom_df)

Mode <- function(x) {
  ux <- unique(x)
  ux[which.max(tabulate(match(x, ux)))]
}

M1_t_mode = Mode(digCom_df$daysSinceOpened)

cat("The mode of M1_t is:", M1_t_mode, ".\n")

M2_t_mode = Mode(digCom_df$daysSincePurchased)

cat("The mode of M2_t is:", M2_t_mode, ".\n")


Y_t_mode = Mode(digCom_df$Order_cnt)

cat("The mode of Y_t is:", Y_t_mode, ".\n")


# scale the mediators


digCom_workdf = data.frame(ID = digCom_df$recipient_id,
                           Recent = digCom_df$Recent, 
                           GENDER = digCom_df$gender,
                           BASELINE_AGE = digCom_df$age, 
                           t = digCom_df$t,
                           Z_t = digCom_df$Discount,
                           D_t = digCom_df$opened, 
                           M1_t = digCom_df$daysSinceOpened,
                           M2_t = digCom_df$daysSincePurchased,
                           Y_t = digCom_df$Order_cnt)


# change GENDER elements from M to 1,and others to 0.
digCom_workdf$GENDER <- ifelse(digCom_workdf$GENDER == "M", 1, 0)


# change BASELINE_AGE elements from >=4 to 1,and <4 to 0.
digCom_workdf$BASELINE_AGE <- ifelse(digCom_workdf$BASELINE_AGE >= 4, 1, 0)


#-------------------------------------------------------------------------------------------------------------
#------------------------------------------Data in wide format------------------------------------------------
#-------------------------------------------------------------------------------------------------------------
setDT(digCom_workdf)

digCom_workdf_wide <- dcast(
  digCom_workdf,
  ID + GENDER + BASELINE_AGE ~ t,
  value.var = c("Z_t", "D_t", "M1_t", "M2_t", "Y_t"),
  fun.aggregate = mean   # or unique, depending on your data
)
head(digCom_workdf_wide)

digCom_workdf_wide = digCom_workdf_wide[!duplicated(ID)]  #remove any duplicated ID rows in the wide format data

digCom_workdf_wide = na.omit(digCom_workdf_wide) #deleting the some rows when converting data from long to wide


cat("The total sample size for the analysis is:", length(unique(digCom_workdf_wide$ID)), "\n")


#-------------------------------------------------------------------------------------------------------------
#------------------------------------------Input data---------------------------------------------------------
#-------------------------------------------------------------------------------------------------------------


#L0 df order columns by intercept, binary covariates, continuous covariates
L0_intercept = rep(1,length(digCom_workdf_wide$ID))
L0_df_wide = data.frame(Intercept = L0_intercept,
                        GENDER = digCom_workdf_wide$GENDER, BASELINE_AGE = digCom_workdf_wide$BASELINE_AGE) 


Y_vec_wide = digCom_workdf_wide$Y_t_3


```


### Define design matrices for parametric regression


```{r}
#L03 = digCom_workdf_wide$GENDER * digCom_workdf_wide$BASELINE_AGE 
#L04 = ifelse(digCom_workdf_wide$GENDER + digCom_workdf_wide$BASELINE_AGE>=1,1,0)
#L05 = sin(digCom_workdf_wide$GENDER+3)

param_reg_mat = data.frame(GENDER = digCom_workdf_wide$GENDER, BASELINE_AGE = digCom_workdf_wide$BASELINE_AGE,
                                    Z_t_1 = digCom_workdf_wide$Z_t_1, D_t_1 = digCom_workdf_wide$D_t_1, M1_t_1 = digCom_workdf_wide$M1_t_1, M2_t_1 = digCom_workdf_wide$M2_t_1,
                                    Z_t_2 = digCom_workdf_wide$Z_t_2, D_t_2 = digCom_workdf_wide$D_t_2, M1_t_2 = digCom_workdf_wide$M1_t_2, M2_t_2 = digCom_workdf_wide$M2_t_2,
                                    Z_t_3 = digCom_workdf_wide$Z_t_3, D_t_3 = digCom_workdf_wide$D_t_3, M1_t_3 = digCom_workdf_wide$M1_t_3, M2_t_3 = digCom_workdf_wide$M2_t_3,
                                    Y_t_3 = digCom_workdf_wide$Y_t_3)


Y_param_reg_design_mat = data.frame(GENDER = digCom_workdf_wide$GENDER, BASELINE_AGE = digCom_workdf_wide$BASELINE_AGE, 
                           Z_t_3 = digCom_workdf_wide$Z_t_3, 
                           D_t_3 = digCom_workdf_wide$D_t_3,
                           M1_t_3 = digCom_workdf_wide$M1_t_3, 
                           M2_t_3 = digCom_workdf_wide$M2_t_3)


M2t3_param_reg_design_mat = data.frame(GENDER = digCom_workdf_wide$GENDER, BASELINE_AGE = digCom_workdf_wide$BASELINE_AGE, 
                                       M2_t_2 = digCom_workdf_wide$M2_t_2,
                                       Z_t_3 = digCom_workdf_wide$Z_t_3,
                                       D_t_3 = digCom_workdf_wide$D_t_3,
                                       M1_t_3 = digCom_workdf_wide$M1_t_3)


M1t3_param_reg_design_mat = data.frame(GENDER = digCom_workdf_wide$GENDER, BASELINE_AGE = digCom_workdf_wide$BASELINE_AGE,
                                       M1_t_2 = digCom_workdf_wide$M1_t_2,
                                       M2_t_2 = digCom_workdf_wide$M2_t_2,
                                       Z_t_3 = digCom_workdf_wide$Z_t_3,
                                       D_t_3 = digCom_workdf_wide$D_t_3)

Dt3_param_reg_design_mat = data.frame(GENDER = digCom_workdf_wide$GENDER, BASELINE_AGE = digCom_workdf_wide$BASELINE_AGE,
                                      D_t_2 = digCom_workdf_wide$D_t_2,
                                      M1_t_2 = digCom_workdf_wide$M1_t_2,
                                      M2_t_2 = digCom_workdf_wide$M2_t_2,
                                      Z_t_3 = digCom_workdf_wide$Z_t_3)


Zt3_param_reg_design_mat = data.frame(GENDER = digCom_workdf_wide$GENDER, BASELINE_AGE = digCom_workdf_wide$BASELINE_AGE,
                                      Z_t_2 = digCom_workdf_wide$Z_t_2,
                                      D_t_2 = digCom_workdf_wide$D_t_2,
                                      M1_t_2 = digCom_workdf_wide$M1_t_2,
                                      M2_t_2 = digCom_workdf_wide$M2_t_2)


M2t2_param_reg_design_mat = data.frame(GENDER = digCom_workdf_wide$GENDER, BASELINE_AGE = digCom_workdf_wide$BASELINE_AGE,
                                        M2_t_1 = digCom_workdf_wide$M2_t_1,
                                       Z_t_2 = digCom_workdf_wide$Z_t_2, 
                                       D_t_2 = digCom_workdf_wide$D_t_2,
                                       M1_t_2 = digCom_workdf_wide$M1_t_2)


M1t2_param_reg_design_mat = data.frame(GENDER = digCom_workdf_wide$GENDER, BASELINE_AGE = digCom_workdf_wide$BASELINE_AGE,
                                        M1_t_1 = digCom_workdf_wide$M1_t_1,
                                        M2_t_1 = digCom_workdf_wide$M2_t_1,
                                        Z_t_2 = digCom_workdf_wide$Z_t_2,
                                        D_t_2 = digCom_workdf_wide$D_t_2)


Dt2_param_reg_design_mat = data.frame(GENDER = digCom_workdf_wide$GENDER, BASELINE_AGE = digCom_workdf_wide$BASELINE_AGE,
                                       D_t_1 = digCom_workdf_wide$D_t_1,
                                      M1_t_1 = digCom_workdf_wide$M1_t_1, 
                                      M2_t_1 = digCom_workdf_wide$M2_t_1,
                                      Z_t_2 = digCom_workdf_wide$Z_t_2)


Zt2_param_reg_design_mat = data.frame(GENDER = digCom_workdf_wide$GENDER, BASELINE_AGE = digCom_workdf_wide$BASELINE_AGE,
                                      Z_t_1 = digCom_workdf_wide$Z_t_1, 
                                      D_t_1 = digCom_workdf_wide$D_t_1,
                                      M1_t_1 = digCom_workdf_wide$M1_t_1,
                                      M2_t_1 = digCom_workdf_wide$M2_t_1)


M2t1_param_reg_design_mat = data.frame(GENDER = digCom_workdf_wide$GENDER, BASELINE_AGE = digCom_workdf_wide$BASELINE_AGE,
                                       Z_t_1 = digCom_workdf_wide$Z_t_1,
                                       D_t_1 = digCom_workdf_wide$D_t_1, 
                                       M1_t_1 = digCom_workdf_wide$M1_t_1)


M1t1_param_reg_design_mat = data.frame(GENDER = digCom_workdf_wide$GENDER, BASELINE_AGE = digCom_workdf_wide$BASELINE_AGE,
                                       Z_t_1 = digCom_workdf_wide$Z_t_1,
                                       D_t_1 = digCom_workdf_wide$D_t_1)


Dt1_param_reg_design_mat = data.frame(GENDER = digCom_workdf_wide$GENDER, BASELINE_AGE = digCom_workdf_wide$BASELINE_AGE,
                                      Z_t_1 = digCom_workdf_wide$Z_t_1)


Zt1_param_reg_design_mat = data.frame(GENDER = digCom_workdf_wide$GENDER, BASELINE_AGE = digCom_workdf_wide$BASELINE_AGE)


longitudinal_data_wide_M2 = data.frame(M2_t_1 = digCom_workdf_wide$M2_t_1,
                                       M2_t_2 = digCom_workdf_wide$M2_t_2,
                                       M2_t_3 = digCom_workdf_wide$M2_t_3)


longitudinal_data_wide_M1 = data.frame(M1_t_1 = digCom_workdf_wide$M1_t_1, 
                                       M1_t_2 = digCom_workdf_wide$M1_t_2,
                                       M1_t_3 = digCom_workdf_wide$M1_t_3)


longitudinal_data_wide_D = data.frame(D_t_1 = digCom_workdf_wide$D_t_1,
                                      D_t_2 = digCom_workdf_wide$D_t_2,
                                      D_t_3 = digCom_workdf_wide$D_t_3)


longitudinal_data_wide_Z = data.frame(Z_t_1 = digCom_workdf_wide$Z_t_1,
                                      Z_t_2 = digCom_workdf_wide$Z_t_2,
                                      Z_t_3 = digCom_workdf_wide$Z_t_3)


#-------------------------------------------------------------------------------
#-------------------------------------------------------------------------------
num_Bin_L0 = 2  # both gender and baseline age are binary

# sample frequency of each Binary column of L0_df_wide
pr_theta_Bin_L0 = as.numeric(colMeans(L0_df_wide[2:3], na.rm = TRUE))

# sample means of each Continuous column of L0_df_wide

# sample variances of each Continuous column of L0_df_wide


```


## Ground truth (parameters) using parametric models

### Nimble model

```{r}


#Record model sum-posterior-log-density

sumLogPostDens <- nimbleFunction(
  name = 'sumLogPostDens',
  contains = sampler_BASE,
  setup = function(model, mvSaved, target, control) {
    stochNodes <- setdiff(model$getNodeNames(stochOnly = TRUE), target)
  },
  run = function() {
    model[[target]] <<- model$getLogProb(stochNodes)
  },
  methods = list( reset = function() {} )
)


# Define a custom distribution for zero-inflated hurdle normal
dzinhurdlenorm <- nimbleFunction(
  run = function(x = double(0), pi = double(0), mu = double(0), sigma = double(0), log = integer(0, default = 0)) {
    returnType(double(0))
    if (sigma <= 0) stop("Sigma must be positive")
    logProb = 0
    if (x == 0) {
      logProb = log(max(1e-10, pi))  # Avoid underflow for pi
    } else {
      # Handle truncation probability
      truncProb = max(1e-10, 1 - pnorm(0, mean = mu, sd = sigma))
      logProb = log(max(1e-10, 1 - pi)) +
        dnorm(x, mean = mu, sd = sigma, log = TRUE) -
        log(truncProb)
    }
    if (log) return(logProb)
    return(exp(logProb))
  }
)


rzinhurdlenorm <- nimbleFunction(
  run = function(n = integer(0), pi = double(0), mu = double(0), sigma = double(0)) {
    returnType(double(0))
    if (n != 1) stop("rzinhurdlenorm only allows n = 1")
    if (runif(1) < pi) {
      return(0)  # Zero-inflated part
    } else {
      x <- -1  # Initialize x to an invalid value for the truncation
      while (x <= 0) {
        x <- rnorm(1, mean = mu, sd = sigma)  # Normal component
      }
      return(x)  # Return the valid sample
    }
  }
)

# Test dzinhurdlenorm
dzinhurdlenorm(0, pi = 0.3, mu = 2, sigma = 1, log = TRUE)

# Test rzinhurdlenorm
rzinhurdlenorm(1, pi = 0.3, mu = 2, sigma = 1)


# Register the Distribution in Nimble
registerDistributions(list(
  dzinhurdlenorm = list(
    BUGSdist = "dzinhurdlenorm(pi, mu, sigma)",
    types = c('value = double(0)', 'pi = double(0)', 'mu = double(0)', 'sigma = double(0)'),
    discrete = FALSE  # Set to TRUE only if the distribution produces integers
  )
))


#######################################################################################
##########################Nimble Code Function##################################################
#######################################################################################

code_DG <- nimbleCode({
  logDens ~ dnorm(0, 1)    ## this distribution does not matter: only need to compute model sum-posterior-log-density

  ##################################################################################
  ##############################Prior distributions#################################
  ##################################################################################


  ##############################Mixture component probabilities######################
    pi_mix[1:K] ~ ddirch(alpha[1:K])


  ##############################Hurdle probabilities################################
    for(c in 1:K){
      pi0_Y[c] ~ dbeta(1,1)
      pi0_M1_t3[c] ~ dbeta(1,1)
      pi0_M2_t3[c] ~ dbeta(1,1)
      pi0_M1_t2[c] ~ dbeta(1,1)
      pi0_M2_t2[c] ~ dbeta(1,1)
      pi0_M1_t1[c] ~ dbeta(1,1)
      pi0_M2_t1[c] ~ dbeta(1,1)
    }


    #####################Regression fixed effects coefficients################################
    for(c in 1:K){
      # AT t =3
      for(k in 1:num_Y_reg_coeff){beta_Yi[c,k] ~ dnorm(mean = 0, var = 10)}
      for(k in 1:num_M2t3_reg_coeff){theta_M2_t3[c,k] ~ dnorm(mean = 0, var = 10)}
      for(k in 1:num_M1t3_reg_coeff){theta_M1_t3[c,k] ~ dnorm(mean = 0, var = 10)}
      for(k in 1:num_Dt3_reg_coeff){theta_D_t3[c,k] ~ dnorm(mean = 0, var = 10)}
      for(k in 1:num_Zt3_reg_coeff){theta_Z_t3[c,k] ~ dnorm(mean = 0, var = 10)}

      # AT t =2
      for(k in 1:num_M2t2_reg_coeff){theta_M2_t2[c,k] ~ dnorm(mean = 0, var = 10)}
      for(k in 1:num_M1t2_reg_coeff){theta_M1_t2[c,k] ~ dnorm(mean = 0, var = 10)}
      for(k in 1:num_Dt2_reg_coeff){theta_D_t2[c,k] ~ dnorm(mean = 0, var = 10)}
      for(k in 1:num_Zt2_reg_coeff){theta_Z_t2[c,k] ~ dnorm(mean = 0, var = 10)}

      # AT t =1
      for(k in 1:num_M2t1_reg_coeff){theta_M2_t1[c,k] ~ dnorm(mean = 0, var = 10)}
      for(k in 1:num_M1t1_reg_coeff){theta_M1_t1[c,k] ~ dnorm(mean = 0, var = 10)}
      for(k in 1:num_Dt1_reg_coeff){theta_D_t1[c,k] ~ dnorm(mean = 0, var = 10)}
      for(k in 1:num_Zt1_reg_coeff){theta_Z_t1[c,k] ~ dnorm(mean = 0, var = 10)}
    }


    #####################Regression variance coefficients################################
    for(c in 1:K){
      sigma_sq_Yi[c] ~ dinvgamma(shape = 3, scale = 1)
      sigma_sq_M2_t3[c] ~ dinvgamma(shape = 3, scale = 1)
      sigma_sq_M1_t3[c] ~ dinvgamma(shape = 3, scale = 1)
      sigma_sq_M2_t2[c] ~ dinvgamma(shape = 3, scale = 1)
      sigma_sq_M1_t2[c] ~ dinvgamma(shape = 3, scale = 1)
      sigma_sq_M2_t1[c] ~ dinvgamma(shape = 3, scale = 1)
      sigma_sq_M1_t1[c] ~ dinvgamma(shape = 3, scale = 1)
    }


    ##################################################################################
    ##############################Likelihood##########################################
    ##################################################################################


    for(i in 1:n) {


    # Mixture component assignment
    s[i] ~ dcat(pi_mix[1:K])


    #AT t = 1

      Zt1[i] ~ dbern(pnorm(inprod(theta_Z_t1[s[i], 1:num_Zt1_reg_coeff], Zt1_param_reg_design_mat[i,1:num_Zt1_reg_coeff]),0,1))
      Dt1[i] ~ dbern(pnorm(inprod(theta_D_t1[s[i], 1:num_Dt1_reg_coeff], Dt1_param_reg_design_mat[i,1:num_Dt1_reg_coeff]),0,1))

      Z_latent_M1t1[i] ~ dbern(1 - pi0_M1_t1[s[i]])  # Indicator for positive values
      m1t1_mean[i] <-   inprod(theta_M1_t1[s[i], 1:num_M1t1_reg_coeff],
                               M1t1_param_reg_design_mat[i, 1:num_M1t1_reg_coeff])
      data_wide_M1t1_pos[i] ~ dnorm(m1t1_mean[i], sd = sqrt(sigma_sq_M1_t1[s[i]]))
      M1t1[i] ~ dnorm(Z_latent_M1t1[i]*data_wide_M1t1_pos[i], sd = 0.25)

      Z_latent_M2t1[i] ~ dbern(1 - pi0_M2_t1[s[i]])  # Indicator for positive values
      m2t1_mean[i] <-   inprod(theta_M2_t1[s[i], 1:num_M2t1_reg_coeff],
                               M2t1_param_reg_design_mat[i, 1:num_M2t1_reg_coeff])
      data_wide_M2t1_pos[i] ~ dnorm(m2t1_mean[i], sd = sqrt(sigma_sq_M2_t1[s[i]]))
      M2t1[i] ~ dnorm(Z_latent_M2t1[i]*data_wide_M2t1_pos[i], sd = 0.25)


    #AT t = 2

      Zt2[i] ~ dbern(pnorm(inprod(theta_Z_t2[s[i], 1:num_Zt2_reg_coeff], Zt2_param_reg_design_mat[i,1:num_Zt2_reg_coeff]),0,1))
      Dt2[i] ~ dbern(pnorm(inprod(theta_D_t2[s[i], 1:num_Dt2_reg_coeff], Dt2_param_reg_design_mat[i,1:num_Dt2_reg_coeff]),0,1))

      Z_latent_M1t2[i] ~ dbern(1 - pi0_M1_t2[s[i]])  # Indicator for positive values
      m1t2_mean[i] <-   inprod(theta_M1_t2[s[i], 1:num_M1t2_reg_coeff],
                               M1t2_param_reg_design_mat[i, 1:num_M1t2_reg_coeff])
      data_wide_M1t2_pos[i] ~ dnorm(m1t2_mean[i], sd = sqrt(sigma_sq_M1_t2[s[i]]))
      M1t2[i] ~ dnorm(Z_latent_M1t2[i]*data_wide_M1t2_pos[i], sd = 0.25)

      Z_latent_M2t2[i] ~ dbern(1 - pi0_M2_t2[s[i]])  # Indicator for positive values
      m2t2_mean[i] <-   inprod(theta_M2_t2[s[i], 1:num_M2t2_reg_coeff],
                               M2t2_param_reg_design_mat[i, 1:num_M2t2_reg_coeff])
      data_wide_M2t2_pos[i] ~ dnorm(m2t2_mean[i], sd = sqrt(sigma_sq_M2_t2[s[i]]))
      M2t2[i] ~ dnorm(Z_latent_M2t2[i]*data_wide_M2t2_pos[i], sd = 0.25)


    #AT t = 3

      Zt3[i] ~ dbern(pnorm(inprod(theta_Z_t3[s[i], 1:num_Zt3_reg_coeff], Zt3_param_reg_design_mat[i,1:num_Zt3_reg_coeff]),0,1))
      Dt3[i] ~ dbern(pnorm(inprod(theta_D_t3[s[i], 1:num_Dt3_reg_coeff], Dt3_param_reg_design_mat[i,1:num_Dt3_reg_coeff]),0,1))

      Z_latent_M1t3[i] ~ dbern(1 - pi0_M1_t3[s[i]])  # Indicator for positive values
      m1t3_mean[i] <-   inprod(theta_M1_t3[s[i], 1:num_M1t3_reg_coeff],
                               M1t3_param_reg_design_mat[i, 1:num_M1t3_reg_coeff])
      data_wide_M1t3_pos[i] ~ dnorm(m1t3_mean[i], sd = sqrt(sigma_sq_M1_t3[s[i]]))
      M1t3[i] ~ dnorm(Z_latent_M1t3[i]*data_wide_M1t3_pos[i], sd = 0.25)

      Z_latent_M2t3[i] ~ dbern(1 - pi0_M2_t3[s[i]])  # Indicator for positive values
      m2t3_mean[i] <-   inprod(theta_M2_t3[s[i], 1:num_M2t3_reg_coeff],
                               M2t3_param_reg_design_mat[i, 1:num_M2t3_reg_coeff])
      data_wide_M2t3_pos[i] ~ dnorm(m2t3_mean[i], sd = sqrt(sigma_sq_M2_t3[s[i]]))
      M2t3[i] ~ dnorm(Z_latent_M2t3[i]*data_wide_M2t3_pos[i], sd = 0.25)

      Z_latent_Y[i] ~ dbern(1 - pi0_Y[s[i]])  # Indicator for positive values
      y_mean[i] <- inprod(beta_Yi[s[i], 1:num_Y_reg_coeff], Y_param_reg_design_mat[i, 1:num_Y_reg_coeff])
      Y_pos[i] ~ dnorm(y_mean[i], sd =  sqrt(sigma_sq_Yi[s[i]]))
      Y[i] ~ dnorm(Z_latent_Y[i]*Y_pos[i], sd = 0.25)


  }
})


#######################################################################################
######################################################################################
#######################################################################################


#######################################################################################
##############Fit Parametric model and save one iter only for data generation##########
#######################################################################################

# one outer cluster and one inner cluster for fitting parametric data
L0_mat = as.matrix(L0_df_wide)
num_L0 =3   # one intercept and 2 L0


K_mix_DG = 10  # Number of mixture components for misspecified DGP. Set to 3 to use a 3-component mixture instead.

constants_DG <- list(n = length(unique(digCom_workdf_wide$ID)), # Number of individuals
                     K = K_mix_DG,                               # Number of mixture components
                     num_Y_reg_coeff = ncol(Y_param_reg_design_mat) + 1, # plus 1 to include the intercept
                     num_M2t3_reg_coeff = ncol(M2t3_param_reg_design_mat) + 1, 
                     num_M1t3_reg_coeff = ncol(M1t3_param_reg_design_mat) + 1, 
                     num_Dt3_reg_coeff = ncol(Dt3_param_reg_design_mat) + 1, 
                     num_Zt3_reg_coeff = ncol(Zt3_param_reg_design_mat) + 1, 
                     num_M2t2_reg_coeff = ncol(M2t2_param_reg_design_mat) + 1,
                     num_M1t2_reg_coeff = ncol(M1t2_param_reg_design_mat) + 1,
                     num_Dt2_reg_coeff =ncol(Dt2_param_reg_design_mat) + 1, 
                     num_Zt2_reg_coeff =ncol(Zt2_param_reg_design_mat) + 1, 
                     num_M2t1_reg_coeff =ncol(M2t1_param_reg_design_mat) + 1, 
                     num_M1t1_reg_coeff =ncol(M1t1_param_reg_design_mat) + 1, 
                     num_Dt1_reg_coeff =ncol(Dt1_param_reg_design_mat) + 1, 
                     num_Zt1_reg_coeff =ncol(Zt1_param_reg_design_mat) + 1
)


data_DG <- list(
  # Dirichlet concentration parameter
  alpha = rep(1, K_mix_DG),

  # regression outcomes
  #### t=3
  Y = digCom_workdf_wide$Y_t_3,
  Z_latent_Y = ifelse(digCom_workdf_wide$Y_t_3 ==0, 0,1),
  M2t3 =  digCom_workdf_wide$M2_t_3,
  M1t3 = digCom_workdf_wide$M1_t_3,
  Z_latent_M2t3 = ifelse(digCom_workdf_wide$M2_t_3 ==0, 0,1),
  Z_latent_M1t3 = ifelse(digCom_workdf_wide$M1_t_3 ==0, 0,1),
  Dt3 = digCom_workdf_wide$D_t_3,
  Zt3 = digCom_workdf_wide$Z_t_3,
  
  
  #### t=2
  M2t2 =  digCom_workdf_wide$M2_t_2,
  M1t2 = digCom_workdf_wide$M1_t_2,
  Z_latent_M2t2 = ifelse(digCom_workdf_wide$M2_t_2 ==0, 0,1),
  Z_latent_M1t2 = ifelse(digCom_workdf_wide$M1_t_2 ==0, 0,1),
  Dt2 = digCom_workdf_wide$D_t_2,
  Zt2 = digCom_workdf_wide$Z_t_2,
  
  
  #### t=1
  M2t1 =  digCom_workdf_wide$M2_t_1,
  M1t1 = digCom_workdf_wide$M1_t_1,
  Z_latent_M2t1 = ifelse(digCom_workdf_wide$M2_t_1 ==0, 0,1),
  Z_latent_M1t1 = ifelse(digCom_workdf_wide$M1_t_1 ==0, 0,1),
  Dt1 = digCom_workdf_wide$D_t_1,
  Zt1 = digCom_workdf_wide$Z_t_1,
  
  
  # data for baseline confounders
  
  
  # regression design matrices
  Y_param_reg_design_mat = cbind(L0_df_wide$Intercept, Y_param_reg_design_mat),
  M2t3_param_reg_design_mat = cbind(L0_df_wide$Intercept, M2t3_param_reg_design_mat),
  M1t3_param_reg_design_mat = cbind(L0_df_wide$Intercept, M1t3_param_reg_design_mat),
  Dt3_param_reg_design_mat = cbind(L0_df_wide$Intercept, Dt3_param_reg_design_mat),
  Zt3_param_reg_design_mat = cbind(L0_df_wide$Intercept, Zt3_param_reg_design_mat),
  M2t2_param_reg_design_mat = cbind(L0_df_wide$Intercept, M2t2_param_reg_design_mat),
  M1t2_param_reg_design_mat = cbind(L0_df_wide$Intercept, M1t2_param_reg_design_mat),
  Dt2_param_reg_design_mat = cbind(L0_df_wide$Intercept, Dt2_param_reg_design_mat),
  Zt2_param_reg_design_mat = cbind(L0_df_wide$Intercept, Zt2_param_reg_design_mat),
  M2t1_param_reg_design_mat = cbind(L0_df_wide$Intercept, M2t1_param_reg_design_mat),
  M1t1_param_reg_design_mat = cbind(L0_df_wide$Intercept, M1t1_param_reg_design_mat),
  Dt1_param_reg_design_mat = cbind(L0_df_wide$Intercept, Dt1_param_reg_design_mat),
  Zt1_param_reg_design_mat = cbind(L0_df_wide$Intercept, Zt1_param_reg_design_mat)
  
  
)


inits_DG <- list(
  # mixture parameters
  pi_mix = rep(1/K_mix_DG, K_mix_DG),
  s = sample(1:K_mix_DG, constants_DG$n, replace = TRUE),

  # outcome model parameters (K x num_coeff matrices)
  beta_Yi = matrix(0, nrow = K_mix_DG, ncol = constants_DG$num_Y_reg_coeff),
  sigma_sq_Yi = rinvgamma(K_mix_DG, 1, 1),
  pi0_Y = rep(0.5, K_mix_DG),
  Y_pos = rep(mean(digCom_workdf_wide$Y_t_3), constants_DG$n),

  # mediator parameters at t =3
  theta_M2_t3 = matrix(0, nrow = K_mix_DG, ncol = constants_DG$num_M2t3_reg_coeff),
  theta_M1_t3 = matrix(0, nrow = K_mix_DG, ncol = constants_DG$num_M1t3_reg_coeff),
  sigma_sq_M2_t3 = rinvgamma(K_mix_DG, 1, 1),
  sigma_sq_M1_t3 = rinvgamma(K_mix_DG, 1, 1),
  pi0_M2_t3 = rep(0.5, K_mix_DG),
  pi0_M1_t3 = rep(0.5, K_mix_DG),
  data_wide_M2t3_pos = rep(mean(digCom_workdf_wide$M2_t_3), constants_DG$n),
  data_wide_M1t3_pos = rep(mean(digCom_workdf_wide$M1_t_3), constants_DG$n),

  # mediator parameters at t =2
  theta_M2_t2 = matrix(0, nrow = K_mix_DG, ncol = constants_DG$num_M2t2_reg_coeff),
  theta_M1_t2 = matrix(0, nrow = K_mix_DG, ncol = constants_DG$num_M1t2_reg_coeff),
  sigma_sq_M2_t2 = rinvgamma(K_mix_DG, 1, 1),
  sigma_sq_M1_t2 = rinvgamma(K_mix_DG, 1, 1),
  pi0_M2_t2 = rep(0.5, K_mix_DG),
  pi0_M1_t2 = rep(0.5, K_mix_DG),
  data_wide_M2t2_pos = rep(mean(digCom_workdf_wide$M2_t_2), constants_DG$n),
  data_wide_M1t2_pos = rep(mean(digCom_workdf_wide$M1_t_2), constants_DG$n),

  # mediator parameters at t =1
  theta_M2_t1 = matrix(0, nrow = K_mix_DG, ncol = constants_DG$num_M2t1_reg_coeff),
  theta_M1_t1 = matrix(0, nrow = K_mix_DG, ncol = constants_DG$num_M1t1_reg_coeff),
  sigma_sq_M2_t1 = rinvgamma(K_mix_DG, 1, 1),
  sigma_sq_M1_t1 = rinvgamma(K_mix_DG, 1, 1),
  pi0_M2_t1 = rep(0.5, K_mix_DG),
  pi0_M1_t1 = rep(0.5, K_mix_DG),
  data_wide_M2t1_pos = rep(mean(digCom_workdf_wide$M2_t_1), constants_DG$n),
  data_wide_M1t1_pos = rep(mean(digCom_workdf_wide$M1_t_1), constants_DG$n),

  # treatment receipt parameters (K x num_coeff matrices)
  theta_D_t3 = matrix(0, nrow = K_mix_DG, ncol = constants_DG$num_Dt3_reg_coeff),
  theta_D_t2 = matrix(0, nrow = K_mix_DG, ncol = constants_DG$num_Dt2_reg_coeff),
  theta_D_t1 = matrix(0, nrow = K_mix_DG, ncol = constants_DG$num_Dt1_reg_coeff),

  # treatment assignment parameters (K x num_coeff matrices)
  theta_Z_t3 = matrix(0, nrow = K_mix_DG, ncol = constants_DG$num_Zt3_reg_coeff),
  theta_Z_t2 = matrix(0, nrow = K_mix_DG, ncol = constants_DG$num_Zt2_reg_coeff),
  theta_Z_t1 = matrix(0, nrow = K_mix_DG, ncol = constants_DG$num_Zt1_reg_coeff)
)


Param_data_generating_model <- nimbleModel(code_DG, constants_DG, data_DG, inits_DG)  # model creation


compile_Param_data_generating_model <- compileNimble(Param_data_generating_model, showCompilerOutput = TRUE)  # model compilation

# MCMC configuration
config_MCMC_DG <- configureMCMC(Param_data_generating_model, useConjugacy = TRUE,
                                enableWAIC = TRUE,
                                monitors = c("pi_mix", "s",
                                             "beta_Yi", "sigma_sq_Yi", "pi0_Y",
                                             "theta_M2_t3", "theta_M1_t3", "sigma_sq_M2_t3", "sigma_sq_M1_t3", "pi0_M2_t3", "pi0_M1_t3",
                                             "theta_M2_t2", "theta_M1_t2", "sigma_sq_M2_t2", "sigma_sq_M1_t2", "pi0_M2_t2", "pi0_M1_t2",
                                             "theta_M2_t1", "theta_M1_t1", "sigma_sq_M2_t1", "sigma_sq_M1_t1", "pi0_M2_t1", "pi0_M1_t1",
                                             "theta_D_t1","theta_D_t2", "theta_D_t3",
                                             "theta_Z_t1","theta_Z_t2", "theta_Z_t3",
                                             "logDens"))


config_MCMC_DG$removeSamplers('logDens')   ## remove sampler assigned to 'logDens'
config_MCMC_DG$addSampler(target = 'logDens', type = 'sumLogPostDens')   ## add our custom sampler


mcmc_DG <- buildMCMC(config_MCMC_DG)
cmcmc_DG <- compileNimble(mcmc_DG, project = Param_data_generating_model, showCompilerOutput = TRUE)

# burn-in 10000 iterations and save 1 iter for data generation
num_iter_DG = 15000;  num_burnin_DG = 10000;  num_thin_DG = 5;  num_chains_DG= 1


samples_allChains_DG <- runMCMC(cmcmc_DG, niter = num_iter_DG, nburnin = num_burnin_DG,
                             nchains = num_chains_DG, 
                             setSeed = TRUE, thin = num_thin_DG, WAIC = TRUE)

post_samples_data_generating_model_list <- samples_allChains_DG$samples   # list of nchains matrices


param_samples_data_generating_model_df <- as.data.frame(post_samples_data_generating_model_list)

# only keep the posterior means of the parameters
colnames(param_samples_data_generating_model) <- colnames(param_samples_data_generating_model_df)


```


## G-Computation

## Code for Parametric G-computation

```{r}

sample_L0_bin_multiple = function(L0_obs_bin_data_no_intercept, # dataframe of all binary baseline confounders
                                  num_MC_samples
){
  
  probs = colMeans(L0_obs_bin_data_no_intercept)  
  
  return_df = as.data.frame(
    matrix(rbinom(num_MC_samples * length(probs), size = 1, prob = rep(probs, each = num_MC_samples)), 
           nrow = num_MC_samples, ncol = length(probs))
  )
  
  
  return(return_df)
  
}


sample_Zt = function(MCdata,                             # MC data upto this point in the temporal order
                     Param_coeffs_df,
                     num_MC_samples,                     # number of MC samples to be generated
                     #num_L0,                             # number of L0 INCLUDING intercept
                     t,                                  # t = {1, ..., T}
                     it,                                 # an integer from 1:Q (number of post iterations)
                     s_vec,                              # component assignments for each MC sample
                     K_mix = 10                           # number of mixture components
){

  num_covs = ncol(MCdata)
  Z_t_prob = rep(NA, num_MC_samples)

  for(cc in 1:K_mix){
    idx = which(s_vec == cc)
    if(length(idx) == 0) next

    # get component-specific parameter samples for this iteration at time = t
    param_coeff_theta_Zt_vec = c()
    for(k in 1:num_covs){
      theta_Zt_colnames_ordered = paste0("theta_Z_t",t,"[",cc,", ",k,"]")
      theta_Zt_colnames = theta_Zt_colnames_ordered[theta_Zt_colnames_ordered %in%
                                                       colnames(Param_coeffs_df)]
      param_coeff_theta_Zt_vec[k] = as.numeric(sapply(theta_Zt_colnames,
                                                      function(col_name) Param_coeffs_df[[col_name]][it]))
    }

    Z_t_prob[idx] = pnorm(as.matrix(MCdata[idx, , drop=FALSE]) %*% param_coeff_theta_Zt_vec)
  }

  Z_t_vec = rbinom(n = num_MC_samples, size = 1, prob = Z_t_prob)

  return(Z_t_vec)

}


sample_Dt = function(MCdata,                             # MC data upto this point in the temporal order
                     Param_coeffs_df,
                     num_MC_samples,                     # number of MC samples to be generated
                     #num_L0,                             # number of L0 INCLUDING intercept
                     t,                                  # t = {1, ..., T}
                     it,                                 # an integer from 1:Q (number of post iterations)
                     s_vec,                              # component assignments for each MC sample
                     K_mix = 10                           # number of mixture components
){

  num_covs = ncol(MCdata)
  D_t_prob = rep(NA, num_MC_samples)

  for(cc in 1:K_mix){
    idx = which(s_vec == cc)
    if(length(idx) == 0) next

    # get component-specific parameter samples for this iteration at time = t
    param_coeff_theta_Dt_vec = c()
    for(k in 1:num_covs){
      theta_Dt_colnames_ordered = paste0("theta_D_t",t,"[",cc,", ",k,"]")
      theta_Dt_colnames = theta_Dt_colnames_ordered[theta_Dt_colnames_ordered %in%
                                                       colnames(Param_coeffs_df)]
      param_coeff_theta_Dt_vec[k] = as.numeric(sapply(theta_Dt_colnames,
                                                      function(col_name) Param_coeffs_df[[col_name]][it]))
    }

    D_t_prob[idx] = pnorm(as.matrix(MCdata[idx, , drop=FALSE]) %*% param_coeff_theta_Dt_vec)
  }

  D_t_vec = rbinom(n = num_MC_samples, size = 1, prob = D_t_prob)

  return(D_t_vec)

}


sample_allMediators_Mt = function(MCdata,                # MC data upto this point in the temporal order
                                  Param_coeffs_df,
                                  num_MC_samples,                     # number of MC samples to be generated
                                  number_of_mediators,                # number of mediators
                                  t,                                  # t = {1, ..., T}
                                  it                                  # an integer from 1:Q (number of post iterations)
){
  
  param_coeff_theta_Mt_mat = matrix(NA, nrow = ncol(MCdata), ncol = number_of_mediators) # each column contains regression mean coeffs for a mediator
  param_coeff_sigSq_Mt_vec = c()
  param_coeff_pi0_Mt_vec = c()
  for(j in 1:number_of_mediators){
    theta_Mt_colnames_ordered = unlist(
      lapply(1:ncol(MCdata), function(k) paste0("theta_M",j,"_t",t,"[",k,"]"))
    )
    
    theta_Mt_colnames =  theta_Mt_colnames_ordered[theta_Mt_colnames_ordered %in%
                                                     colnames(Param_coeffs_df)]
    #df with nrow = N.M, ncol = num_L0
    param_coeff_theta_Mt_mat[,j] = as.numeric(sapply(theta_Mt_colnames, 
                                                     function(col_name) Param_coeffs_df[[col_name]][it]))
    
    
    sigSq_Mt_colnames_ordered = paste0("sigma_sq_M",j,"_t",t)
    
    sigSq_Mt_colnames =  sigSq_Mt_colnames_ordered[sigSq_Mt_colnames_ordered %in%
                                                     colnames(Param_coeffs_df)]
    #df with nrow = N.M, ncol = num_L0
    param_coeff_sigSq_Mt_vec[j] = as.numeric(sapply(sigSq_Mt_colnames, 
                                                    function(col_name) Param_coeffs_df[[col_name]][it]))
    
    
    pi0_Mt_colnames_ordered = paste0("pi0_M",j,"_t",t)
    
    pi0_Mt_colnames =  pi0_Mt_colnames_ordered[pi0_Mt_colnames_ordered %in%
                                                 colnames(Param_coeffs_df)]
    
    param_coeff_pi0_Mt_vec[j] = as.numeric(sapply(pi0_Mt_colnames, 
                                                  function(col_name) Param_coeffs_df[[col_name]][it]))
    
    
  }
  
  
  ##################Get coeffs for the random effects###############################
  Sigma_b_M1M2_t_col_name = sapply(1:number_of_mediators, function(mediator_num) {
    paste0("Sigma_b_M1M2_t",t,"[", mediator_num, ", ", 1:number_of_mediators, "]")  # Column names for Sigma_b_M1M2_t1[1,1] to Sigma_b_M1M2_t1[2,2]
  })
  
  # matrix of dimension J by J for J mediators
  Sigma_b_M1M2_t_mat = apply(Sigma_b_M1M2_t_col_name, c(1,2),
                             function(col_name){Param_coeffs_df[[col_name]][it]}) 
  
  #b_M1M2_t_df is a df of dimensions num_MC_samples by length(zero_vec)
  b_M1M2_t_mat = as.matrix(rmvnorm(n = num_MC_samples, mean = zero_vec, sigma = Sigma_b_M1M2_t_mat))   #random intercepts
  
  
  # Generate both M1 and M2
  
  #M1M2_pos_indicator_df is a df of dimensions num_MC_samples by length(zero_vec)
  M1M2_pos_indicator_df =  as.data.frame(
    matrix(rbinom(num_MC_samples * length(param_coeff_pi0_Mt_vec), 
                  size = 1, 
                  prob = rep(1-param_coeff_pi0_Mt_vec, each = num_MC_samples)),
           nrow = num_MC_samples, ncol = length(param_coeff_pi0_Mt_vec))
  )
  
  M1M2_pos_mean_df = (as.matrix(MCdata) %*% param_coeff_theta_Mt_mat) +  b_M1M2_t_mat # Result: [num_MC_samples × num_of_mediators]
  
  truncnorm_samples = matrix(NA, nrow = num_MC_samples, ncol = number_of_mediators)
  for (j in 1:number_of_mediators) {
    truncnorm_samples[, j] = rtruncnorm(
      n = num_MC_samples,
      a = 0,                
      b = Inf,                 
      mean = M1M2_pos_mean_df[, j],     
      sd = sqrt(param_coeff_sigSq_Mt_vec[j])           
    ) * M1M2_pos_indicator_df[,j]
  }
  
  
  return_df = as.data.frame(truncnorm_samples)
  return(return_df)
}


sample_Mediator_Mt = function(MCdata,                # MC data upto this point in the temporal order
                              Param_coeffs_df,
                              num_MC_samples,                     # number of MC samples to be generated
                              mediator_number,                   # 1 to J (num of mediators)
                              t,                                  # t = {1, ..., T}
                              it,                                 # an integer from 1:Q (number of post iterations)
                              s_vec,                              # component assignments for each MC sample
                              K_mix = 10                           # number of mixture components
){

  num_covs = ncol(MCdata)
  Mt_pos_mean_vec = rep(NA, num_MC_samples)
  Mt_pos_indicator = rep(NA, num_MC_samples)
  Mt_sigma_sq = rep(NA, num_MC_samples)

  for(cc in 1:K_mix){
    idx = which(s_vec == cc)
    if(length(idx) == 0) next

    # get component-specific regression coefficients
    param_coeff_theta_Mt_vec = c()
    for(k in 1:num_covs){
      theta_Mt_colnames_ordered = paste0("theta_M",mediator_number,"_t",t,"[",cc,", ",k,"]")
      theta_Mt_colnames = theta_Mt_colnames_ordered[theta_Mt_colnames_ordered %in%
                                                       colnames(Param_coeffs_df)]
      param_coeff_theta_Mt_vec[k] = as.numeric(sapply(theta_Mt_colnames,
                                                      function(col_name) Param_coeffs_df[[col_name]][it]))
    }

    # get component-specific sigma_sq
    sigSq_Mt_col = paste0("sigma_sq_M",mediator_number,"_t",t,"[",cc,"]")
    param_coeff_sigSq_Mt = as.numeric(Param_coeffs_df[[sigSq_Mt_col]][it])

    # get component-specific pi0
    pi0_Mt_col = paste0("pi0_M",mediator_number,"_t",t,"[",cc,"]")
    param_coeff_pi0_Mt = as.numeric(Param_coeffs_df[[pi0_Mt_col]][it])

    Mt_pos_mean_vec[idx] = as.matrix(MCdata[idx, , drop=FALSE]) %*% param_coeff_theta_Mt_vec
    Mt_pos_indicator[idx] = rbinom(n = length(idx), size = 1, prob = 1 - param_coeff_pi0_Mt)
    Mt_sigma_sq[idx] = param_coeff_sigSq_Mt
  }

  truncnorm_samples = rtruncnorm(
    n = num_MC_samples,
    a = 0,
    b = 10,
    mean = Mt_pos_mean_vec,
    sd = sqrt(Mt_sigma_sq)
  ) * Mt_pos_indicator

  return(as.numeric(truncnorm_samples))
}


compute_Y_mean = function(MCdata,                # MC data upto this point in the temporal order
                          Param_coeffs_df,
                          num_MC_samples,                     # number of MC samples to be generated
                          it,                                 # an integer from 1:Q (number of post iterations)
                          s_vec,                              # component assignments for each MC sample
                          K_mix = 10                           # number of mixture components
){

  num_covs = ncol(MCdata)
  Y_pos_mean_vec = rep(NA, num_MC_samples)
  param_coeff_sigSq_Yi_vec = rep(NA, num_MC_samples)
  param_coeff_pi0_Y_vec = rep(NA, num_MC_samples)

  for(cc in 1:K_mix){
    idx = which(s_vec == cc)
    if(length(idx) == 0) next

    # get component-specific regression coefficients
    param_coeff_beta_Yi_vec = c()
    for(k in 1:num_covs){
      beta_Yi_colnames_ordered = paste0("beta_Yi[",cc,", ",k,"]")
      beta_Yi_colnames = beta_Yi_colnames_ordered[beta_Yi_colnames_ordered %in%
                                                     colnames(Param_coeffs_df)]
      param_coeff_beta_Yi_vec[k] = as.numeric(sapply(beta_Yi_colnames,
                                                     function(col_name) Param_coeffs_df[[col_name]][it]))
    }

    # get component-specific sigma_sq
    sigSq_Yi_col = paste0("sigma_sq_Yi[",cc,"]")
    param_coeff_sigSq_cc = as.numeric(Param_coeffs_df[[sigSq_Yi_col]][it])

    # get component-specific pi0
    pi0_Y_col = paste0("pi0_Y[",cc,"]")
    param_coeff_pi0_cc = as.numeric(Param_coeffs_df[[pi0_Y_col]][it])

    Y_pos_mean_vec[idx] = as.matrix(MCdata[idx, , drop=FALSE]) %*% param_coeff_beta_Yi_vec
    param_coeff_sigSq_Yi_vec[idx] = param_coeff_sigSq_cc
    param_coeff_pi0_Y_vec[idx] = param_coeff_pi0_cc
  }


  #compute mean of truncated Normal
  z = -Y_pos_mean_vec/sqrt(param_coeff_sigSq_Yi_vec)
  phi_z = dnorm(z)  # PDF of the standard normal at z
  Phi_z = pnorm(z)  # CDF of the standard normal at z
  trunc_norm_param_denom = pmax(1 - Phi_z, 1e-10)
  trunc_norm_mean_vec = Y_pos_mean_vec + (phi_z / trunc_norm_param_denom) * sqrt(param_coeff_sigSq_Yi_vec)


  # E[Y|...] = (1-pi0) * E[trunc_norm]
  mean_Y_hurdle = trunc_norm_mean_vec * (1 - param_coeff_pi0_Y_vec)

  return(mean_Y_hurdle)
}


####################################################################
######.............Function for MC integration .............########
MCInteg <- function(var.type, # Vector of variable specifications for data.  Fi=fixed (e.g. the exposure), D=trt received, M1= mediator 1,  M2= mediator 2, Y=outcome.
                    Param_coeffs, #fitted BNP model parameter samples list
                    fixed.regime.trt, # A vector specifying the Exposure  regime Z
                    fixed.regime.control, # A vector specifying the Exposure  regime Z_star
                    U1,       # could be one of: "c" for VALUE ATTENTIVE, "d" for PRICE ATTENTIVE, "n" for NON-ACTIVE CUSTOMERS and "a" for ACTIVE CUSTOMERS
                    J=10000, # Size of pseudo data. Default is set to 2,000.
                    Ndraws=1000, # Number of posterior draws. Default is set to 200.
                    L0_obs_data_no_intercept, #matrix of all baseline confounders excluding the intercept
                    num_Bin_L0,
                    num_Cont_L0,
                    max_t,
                    K_mix = 10, # number of mixture components
                    ...
){
  
  n_Y <- length(which(var.type=="Y")) # Number of outcome variables, should be equal to 1
  n_L0 <- length(which(var.type=="L0")) # Number of baseline confounder variables INCLUDING the intercept, >1 allowed
  n_Fi <- length(which(var.type=="Fi")) # Number of fixed variables, >1 allowed
  if(!is.null(fixed.regime.trt)) {
    n_Reg_trt <- max(ifelse(!is.null(fixed.regime.trt), length(fixed.regime.trt), 0))
  } else {
    n_Reg_trt <- 1
  }
  
  if(!is.null(fixed.regime.control)) {
    n_Reg_control <- max(ifelse(!is.null(fixed.regime.control), length(fixed.regime.control), 0))
  } else {
    n_Reg_control <- 1
  }
  
  if (n_Y != 1) stop("The number of outcome variables is not equal to 1 ")
  #if (ncol(data) != length(var.type)) stop("The number of columns in data is not equal to the length of var.type ")
  
  if(!is.null(fixed.regime.trt)){
    if (length(fixed.regime.trt) != n_Fi) stop("Warning: The number of fixed variables is not equal to the length of the fixed regime(s)")
  }
  
  if(!is.null(fixed.regime.control)){
    if (length(fixed.regime.control) != n_Fi) stop("Warning: The number of fixed variables is not equal to the length of the fixed regime(s)")
  }
  
  if (!(U1 %in% c("c", "d", "n", "a"))) {
    stop("U1 must be one of 'c', 'd', 'n', or 'a'")
  }
  
  
  ########################################################
  ## Create matrices to store the output. 
  
  
  Y_zzstar_mat <- matrix(nrow =  1 , ncol = Ndraws)
  MC_error_vec = c()
  
  
  for(it in 1:Ndraws) {
    zt <- 1                               # zt indexes FIXED longitudinal trt regime in G-comp
    dt <- 1
    mt <- 1
    intercept = rep(1, J)
    
    
    ################### We only have binary L0 in replicated dataframe###########################################   
    L0_bin_sampled_mat_iter = NULL # initialize a matrix to store samples
    L0_bin_sampled_mat_iter = sample_L0_bin_multiple(L0_obs_bin_data_no_intercept = L0_obs_data_no_intercept[, 1:num_Bin_L0], 
                                                     num_MC_samples= J)
    L0_data = cbind(intercept, L0_bin_sampled_mat_iter)

    # Sample mixture component assignments for this iteration
    pi_mix_cols = paste0("pi_mix[", 1:K_mix, "]")
    pi_mix_vec = as.numeric(sapply(pi_mix_cols, function(col_name) Param_coeffs[[col_name]][it]))
    s_vec = sample(1:K_mix, size = J, replace = TRUE, prob = pi_mix_vec)


    # design matrix for regression (initialize with L0_data)
    
    Zt_mat_MCdata_trt = matrix(NA, nrow = J, ncol = max_t)
    Dt_mat_MCdata_trt = matrix(NA, nrow = J, ncol = max_t)
    M1t_mat_MCdata_trt = matrix(NA, nrow = J, ncol = max_t)
    M2t_mat_MCdata_trt = matrix(NA, nrow = J, ncol = max_t)
    
    
    Zt_mat_MCdata_control = matrix(NA, nrow = J, ncol = max_t)
    Dt_mat_MCdata_control = matrix(NA, nrow = J, ncol = max_t)
    M1t_mat_MCdata_control = matrix(NA, nrow = J, ncol = max_t)
    M2t_mat_MCdata_control = matrix(NA, nrow = J, ncol = max_t)
    
    
    Z1_trt = rep(fixed.regime.trt[1], J)
    Z1_control = rep(fixed.regime.control[1], J)
    
    if (U1 == "c") {
      D1_trt = Z1_trt
      D1_control = Z1_control
    } else if (U1 == "d") {
      D1_trt = 1- Z1_trt
      D1_control = 1-Z1_control
    } else if (U1 == "n") {
      D1_trt = rep(0,J)
      D1_control = rep(0,J)
    } else if (U1 == "a") {
      D1_trt = rep(1,J)
      D1_control = rep(1,J)
    }
    
    
    for (j in (n_L0+1):length(var.type)) {                                         
      
      if(var.type[j] == "Fi") {
        Zt_mat_MCdata_trt[,zt] = rep(fixed.regime.trt[zt], J)
        Zt_mat_MCdata_control[,zt] = rep(fixed.regime.control[zt], J)
        zt = zt + 1
      }
      else if(var.type[j] == "Dt") {
        
        if(dt == 1){
          Dt_mat_MCdata_trt[,dt] = D1_trt
          Dt_mat_MCdata_control[,dt] = D1_control
        }else{
          Dt_sampled_vec_iter_trt =sample_Dt(MCdata = cbind(L0_data, Dt_mat_MCdata_trt[,dt-1],
                                                            M1t_mat_MCdata_trt[,dt-1], M2t_mat_MCdata_trt[,dt-1],
                                                            Zt_mat_MCdata_trt[,dt]),                             
                                             Param_coeffs_df = Param_coeffs,
                                             num_MC_samples = J,                     
                                             t = dt,
                                             it = it,
                                             s_vec = s_vec, K_mix = K_mix)
          Dt_sampled_vec_iter_control =sample_Dt(MCdata = cbind(L0_data, Dt_mat_MCdata_control[,dt-1],
                                                                M1t_mat_MCdata_control[,dt-1], M2t_mat_MCdata_control[,dt-1],
                                                                Zt_mat_MCdata_control[,dt]),                            
                                                 Param_coeffs_df = Param_coeffs,
                                                 num_MC_samples = J,                     
                                                 t = dt,
                                                 it = it,
                                                 s_vec = s_vec, K_mix = K_mix)
          
          
          Dt_mat_MCdata_trt[,dt] =  Dt_sampled_vec_iter_trt
          Dt_mat_MCdata_control[,dt] =  Dt_sampled_vec_iter_control
        }
        dt = dt +1
      }
      else if(var.type[j] == "M1t") { 
        if(mt == 1){
          M1t_sampled_vec_iter_trt = sample_Mediator_Mt(MCdata = cbind(L0_data, Zt_mat_MCdata_trt[,1], Dt_mat_MCdata_trt[,1]),
                                                        Param_coeffs_df = Param_coeffs,
                                                        num_MC_samples = J,                     
                                                        mediator_number =  1,                
                                                        t = mt,
                                                        it = it,
                                                        s_vec = s_vec, K_mix = K_mix)
            
            
          M1t_sampled_vec_iter_control =sample_Mediator_Mt(MCdata = cbind(L0_data, Zt_mat_MCdata_control[,1], Dt_mat_MCdata_control[,1]),
                                                           Param_coeffs_df = Param_coeffs,
                                                           num_MC_samples = J,                     
                                                           mediator_number =  1,                
                                                           t = mt,
                                                           it = it,
                                                           s_vec = s_vec, K_mix = K_mix)
          
          
          M1t_mat_MCdata_trt[,1] =  M1t_sampled_vec_iter_trt
          M1t_mat_MCdata_control[,1] =  M1t_sampled_vec_iter_control
          
        }else{
          M1t_sampled_vec_iter_trt = sample_Mediator_Mt(MCdata = cbind(L0_data, M1t_mat_MCdata_trt[,mt-1], M2t_mat_MCdata_trt[,mt-1],
                                                                       Zt_mat_MCdata_trt[,mt], Dt_mat_MCdata_trt[,mt]),
                                                        Param_coeffs_df = Param_coeffs,
                                                        num_MC_samples = J,                     
                                                        mediator_number =  1,                
                                                        t = mt,
                                                        it = it,
                                                        s_vec = s_vec, K_mix = K_mix)
          
          
          M1t_sampled_vec_iter_control =sample_Mediator_Mt(MCdata = cbind(L0_data, M1t_mat_MCdata_control[,mt-1], M2t_mat_MCdata_control[,mt-1],
                                                                          Zt_mat_MCdata_control[,mt], Dt_mat_MCdata_control[,mt]),
                                                           Param_coeffs_df = Param_coeffs,
                                                           num_MC_samples = J,                     
                                                           mediator_number =  1,                
                                                           t = mt,
                                                           it = it,
                                                           s_vec = s_vec, K_mix = K_mix)
          
          
          M1t_mat_MCdata_trt[,mt] =  M1t_sampled_vec_iter_trt
          M1t_mat_MCdata_control[,mt] =  M1t_sampled_vec_iter_control  
        }
        
        
      }
      else if(var.type[j] == "M2t") { 
        if(mt == 1){
          M2t_sampled_vec_iter_trt = sample_Mediator_Mt(MCdata = cbind(L0_data, Zt_mat_MCdata_trt[,1], Dt_mat_MCdata_trt[,1],
                                                                       M1t_mat_MCdata_trt[,1]),
                                                        Param_coeffs_df = Param_coeffs,
                                                        num_MC_samples = J,                     
                                                        mediator_number =  2,                
                                                        t = mt,
                                                        it = it,
                                                        s_vec = s_vec, K_mix = K_mix)
          
          
          M2t_sampled_vec_iter_control =sample_Mediator_Mt(MCdata = cbind(L0_data, Zt_mat_MCdata_control[,1], Dt_mat_MCdata_control[,1],
                                                                          M1t_mat_MCdata_control[,1]),
                                                           Param_coeffs_df = Param_coeffs,
                                                           num_MC_samples = J,                     
                                                           mediator_number =  2,                
                                                           t = mt,
                                                           it = it,
                                                           s_vec = s_vec, K_mix = K_mix)
          
          M2t_mat_MCdata_trt[,1] =  M2t_sampled_vec_iter_trt
          M2t_mat_MCdata_control[,1] =  M2t_sampled_vec_iter_control
          
          
        }else{
          M2t_sampled_vec_iter_trt = sample_Mediator_Mt(MCdata = cbind(L0_data, M2t_mat_MCdata_trt[,mt-1],
                                                                       Zt_mat_MCdata_trt[,mt], Dt_mat_MCdata_trt[,mt],
                                                                       M1t_mat_MCdata_trt[,mt]),
                                                        Param_coeffs_df = Param_coeffs,
                                                        num_MC_samples = J,                     
                                                        mediator_number =  2,                
                                                        t = mt,
                                                        it = it,
                                                        s_vec = s_vec, K_mix = K_mix)
          
          
          M2t_sampled_vec_iter_control =sample_Mediator_Mt(MCdata = cbind(L0_data,  M2t_mat_MCdata_control[,mt-1],
                                                                          Zt_mat_MCdata_control[,mt], Dt_mat_MCdata_control[,mt],
                                                                          M1t_mat_MCdata_control[,mt]),
                                                           Param_coeffs_df = Param_coeffs,
                                                           num_MC_samples = J,                     
                                                           mediator_number =  2,                
                                                           t = mt,
                                                           it = it,
                                                           s_vec = s_vec, K_mix = K_mix)
          
          M2t_mat_MCdata_trt[,mt] =  M2t_sampled_vec_iter_trt
          M2t_mat_MCdata_control[,mt] =  M2t_sampled_vec_iter_control 
          
        }
        
        
        mt = mt + 1
        
      }
      
      else if(var.type[j] == "Y") {
        Y_mean_vec = compute_Y_mean(MCdata = cbind(L0_data,  
                                                   Zt_mat_MCdata_trt[,ncol(Zt_mat_MCdata_trt)],
                                                   Dt_mat_MCdata_trt[,ncol(Dt_mat_MCdata_trt)],
                                                   M1t_mat_MCdata_control[,ncol(M1t_mat_MCdata_control)],
                                                   M2t_mat_MCdata_control[,ncol(M2t_mat_MCdata_control)]),                
                                    Param_coeffs_df = Param_coeffs,
                                    num_MC_samples = J,
                                    it = it,
                                    s_vec = s_vec, K_mix = K_mix)
        
        
        Y_zzstar_mat[1,it] = mean(Y_mean_vec)
        MC_error_vec[it] = sd(Y_mean_vec) / sqrt(length(Y_mean_vec))
        if(it == 500){
          mc_error = sd(Y_mean_vec) / sqrt(length(Y_mean_vec))
        }
      }
    }
  }
  MC_error_to_post_SD = MC_error_vec/ sd(as.numeric(Y_zzstar_mat[1,]))
  return(Y_zzstar_mat)
}


compute_PIDE = function(theta_10, theta_00){
  return(theta_10 - theta_00)
}

compute_PJIIE = function(theta_11, theta_10){
  return(theta_11 - theta_10)
}

compute_PJIIE2 = function(PCE, PIDE){
  return(PCE - PIDE)
}


compute_PCE = function(PIDE, PJIIE){
  return(PIDE+PJIIE)
}

compute_total_effects = function(theta_11, theta_00){
  return(theta_11 - theta_00)
}


calculate_95bayesian_credible_interval  = function(data_row){
  posterior_samples = as.numeric(data_row)
  posterior_mean =  as.numeric(format(round(mean(posterior_samples) , 4), nsmall = 4))
  #posterior_median =  as.numeric(format(round(median(posterior_samples) , 4), nsmall = 4))
  quantiles = quantile(posterior_samples, c(0.025, 0.975))
  interval = as.numeric(format(round(quantiles, 4), nsmall = 4))
  return_df = data.frame(posterior_mean = posterior_mean, 
                         lower_95CI = interval[1],   upper_95CI = interval[2])
  return(return_df)
}


plot_ConfInt <-function(conf_int_mat) {
  conf_int_df = data.frame(conf_int_mat)
  conf_int_df$CI <- 1:nrow(conf_int_df)
  ci_long <- reshape(conf_int_df,
                     direction = "long",
                     varying = setdiff(names(conf_int_df), "CI"),
                     v.names = "Value",
                     timevar = "Bound",
                     times = setdiff(names(conf_int_df), "CI"))
  ggplot(ci_long, aes(x = CI, ymin = Value, ymax = Value, color = Bound )) +
    geom_errorbar(width = 0.2)+
    labs(x = "Visits", y = "Confidence/Credible Intervals")+
    scale_color_manual(values = c("lower" = "red", "upper" = "blue")) +
    theme_minimal()
  
}


## Function Call
```{r}

input_varType1 = c("L0","L0","L0", "Fi", "Dt", "M1t","M2t", "Fi", "Dt", "M1t","M2t","Fi", "Dt", "M1t","M2t", "Y")


#########################################ACTIVE CUSTOMERS#################################################


active_customer_theta_zzstar = MCInteg(var.type = input_varType1,
                                    Param_coeffs = param_samples_data_generating_model_df,
                                    fixed.regime.trt = rep(1,3),
                                    fixed.regime.control = rep(0,3),
                                    U1 = "a",            
                                    J=10000, 
                                    Ndraws= 1000, 
                                    L0_obs_data_no_intercept = L0_df_wide[2:3],
                                    num_Bin_L0 = 2, 
                                    num_Cont_L0 = 0,
                                    max_t = 3)


active_customer_theta_zz = MCInteg(var.type = input_varType1,
                                Param_coeffs = param_samples_data_generating_model_df,
                                fixed.regime.trt = rep(1,3),
                                fixed.regime.control = rep(1,3),
                                U1 = "a",
                                J=10000, 
                                Ndraws= 1000, 
                                L0_obs_data_no_intercept = L0_df_wide[2:3],
                                num_Bin_L0 = 2, 
                                num_Cont_L0 = 0,
                                max_t = 3)


active_customer_theta_zstarzstar = MCInteg(var.type = input_varType1,
                                        Param_coeffs = param_samples_data_generating_model_df,
                                        fixed.regime.trt = rep(0,3),
                                        fixed.regime.control = rep(0,3),
                                        U1 = "a",
                                        J=10000, 
                                        Ndraws= 1000, 
                                    L0_obs_data_no_intercept = L0_df_wide[2:3],
                                    num_Bin_L0 = 2, 
                                    num_Cont_L0 = 0,
                                    max_t = 3)


active_customer_PIDE = compute_PIDE(active_customer_theta_zzstar, active_customer_theta_zstarzstar)
active_customer_PIDE = mean(active_customer_PIDE, na.rm = TRUE)


active_customer_PCE = compute_total_effects(active_customer_theta_zz,active_customer_theta_zstarzstar)
active_customer_PCE = mean(active_customer_PCE, na.rm = TRUE)


active_customer_PJIIE = compute_PJIIE2(active_customer_PCE, active_customer_PIDE)
active_customer_PJIIE = mean(active_customer_PJIIE, na.rm = TRUE)


#########################################Value Attentive#################################################


value_attentive_theta_zzstar = MCInteg(var.type = input_varType1,
                                    Param_coeffs = param_samples_data_generating_model_df,
                                    fixed.regime.trt = rep(1,3),
                                    fixed.regime.control = rep(0,3),
                                    U1 = "c",            
                                    J=10000, 
                                    Ndraws= 1000, 
                                    L0_obs_data_no_intercept = L0_df_wide[2:3],
                                    num_Bin_L0 = 2, 
                                    num_Cont_L0 = 0,
                                    max_t = 3)


value_attentive_theta_zz = MCInteg(var.type = input_varType1,
                                Param_coeffs = param_samples_data_generating_model_df,
                                fixed.regime.trt = rep(1,3),
                                fixed.regime.control = rep(1,3),
                                U1 = "c",
                                J=10000, 
                                Ndraws= 1000, 
                                L0_obs_data_no_intercept = L0_df_wide[2:3],
                                    num_Bin_L0 = 2, 
                                    num_Cont_L0 = 0,
                                    max_t = 3)


value_attentive_theta_zstarzstar = MCInteg(var.type = input_varType1,
                                        Param_coeffs = param_samples_data_generating_model_df,
                                        fixed.regime.trt = rep(0,3),
                                        fixed.regime.control = rep(0,3),
                                        U1 = "c",
                                        J=10000, 
                                        Ndraws= 1000, 
                                    L0_obs_data_no_intercept = L0_df_wide[2:3],
                                    num_Bin_L0 = 2, 
                                    num_Cont_L0 = 0,
                                    max_t = 3)


value_attentive_PIDE = compute_PIDE(value_attentive_theta_zzstar, value_attentive_theta_zstarzstar)
value_attentive_PIDE = mean(value_attentive_PIDE, na.rm = TRUE)


value_attentive_PCE = compute_total_effects(value_attentive_theta_zz,value_attentive_theta_zstarzstar)
value_attentive_PCE = mean(value_attentive_PCE, na.rm = TRUE)


value_attentive_PJIIE = compute_PJIIE2(value_attentive_PCE, value_attentive_PIDE)
value_attentive_PJIIE = mean(value_attentive_PJIIE, na.rm = TRUE)


#########################################Price Attentive#################################################


price_attentive_theta_zzstar = MCInteg(var.type = input_varType1,
                                Param_coeffs = param_samples_data_generating_model_df,
                                fixed.regime.trt = rep(1,3),
                                fixed.regime.control = rep(0,3),
                                U1 = "d",            
                                J=10000, 
                                Ndraws= 1000, 
                                L0_obs_data_no_intercept = L0_df_wide[2:3],
                                    num_Bin_L0 = 2, 
                                    num_Cont_L0 = 0,
                                    max_t = 3)


price_attentive_theta_zz = MCInteg(var.type = input_varType1,
                            Param_coeffs = param_samples_data_generating_model_df,
                            fixed.regime.trt = rep(1,3),
                            fixed.regime.control = rep(1,3),
                            U1 = "d",
                            J=10000, 
                            Ndraws= 1000, 
                            L0_obs_data_no_intercept = L0_df_wide[2:3],
                                    num_Bin_L0 = 2, 
                                    num_Cont_L0 = 0,
                                    max_t = 3)


price_attentive_theta_zstarzstar = MCInteg(var.type = input_varType1,
                                    Param_coeffs = param_samples_data_generating_model_df,
                                    fixed.regime.trt = rep(0,3),
                                    fixed.regime.control = rep(0,3),
                                    U1 = "d",
                                    J=10000, 
                                    Ndraws= 1000, 
                                    L0_obs_data_no_intercept = L0_df_wide[2:3],
                                    num_Bin_L0 = 2, 
                                    num_Cont_L0 = 0,
                                    max_t = 3)


price_attentive_PIDE = compute_PIDE(price_attentive_theta_zzstar, price_attentive_theta_zstarzstar)
price_attentive_PIDE = mean(price_attentive_PIDE, na.rm = TRUE)


price_attentive_PCE = compute_total_effects(price_attentive_theta_zz,price_attentive_theta_zstarzstar)
price_attentive_PCE = mean(price_attentive_PCE, na.rm = TRUE)


price_attentive_PJIIE = compute_PJIIE2(price_attentive_PCE, price_attentive_PIDE)
price_attentive_PJIIE = mean(price_attentive_PJIIE, na.rm = TRUE)


#########################################Non-Active Customers#################################################


non_active_customer_theta_zzstar = MCInteg(var.type = input_varType1,
                              Param_coeffs = param_samples_data_generating_model_df,
                              fixed.regime.trt = rep(1,3),
                              fixed.regime.control = rep(0,3),
                              U1 = "n",            
                              J=10000, 
                              Ndraws= 1000, 
                              L0_obs_data_no_intercept = L0_df_wide[2:3],
                                    num_Bin_L0 = 2, 
                                    num_Cont_L0 = 0,
                                    max_t = 3)


non_active_customer_theta_zz = MCInteg(var.type = input_varType1,
                          Param_coeffs = param_samples_data_generating_model_df,
                          fixed.regime.trt = rep(1,3),
                          fixed.regime.control = rep(1,3),
                          U1 = "n",
                          J=10000, 
                          Ndraws= 1000, 
                          L0_obs_data_no_intercept = L0_df_wide[2:3],
                                    num_Bin_L0 = 2, 
                                    num_Cont_L0 = 0,
                                    max_t = 3)


non_active_customer_theta_zstarzstar = MCInteg(var.type = input_varType1,
                                  Param_coeffs = param_samples_data_generating_model_df,
                                  fixed.regime.trt = rep(0,3),
                                  fixed.regime.control = rep(0,3),
                                  U1 = "n",
                                  J=10000, 
                                  Ndraws= 1000, 
                                  L0_obs_data_no_intercept = L0_df_wide[2:3],
                                    num_Bin_L0 = 2, 
                                    num_Cont_L0 = 0,
                                    max_t = 3)


non_active_customer_PIDE = compute_PIDE(non_active_customer_theta_zzstar, non_active_customer_theta_zstarzstar)
non_active_customer_PIDE = mean(non_active_customer_PIDE, na.rm = TRUE)

 
non_active_customer_PCE = compute_total_effects(non_active_customer_theta_zz,non_active_customer_theta_zstarzstar)
non_active_customer_PCE = mean(non_active_customer_PCE, na.rm = TRUE)


non_active_customer_PJIIE = compute_PJIIE2(non_active_customer_PCE, non_active_customer_PIDE)
non_active_customer_PJIIE = mean(non_active_customer_PJIIE, na.rm = TRUE)


row_names = c("active_customers", "value_attentive", "price_attentive", "non_active_customers")
direct_effects = c(active_customer_PIDE, value_attentive_PIDE, price_attentive_PIDE, non_active_customer_PIDE)
indirect_effects = c(active_customer_PJIIE, value_attentive_PJIIE, price_attentive_PJIIE, non_active_customer_PJIIE)
total_effects = c(active_customer_PCE, value_attentive_PCE, price_attentive_PCE, non_active_customer_PCE)


true_causal_estimands = data.frame(PIDE = direct_effects, PJIIE= indirect_effects, PCE= total_effects)
rownames(true_causal_estimands) = row_names
true_causal_estimands


###############################################################

```


## Results after running the simulation 500 times


```{r}
library(ggplot2)
library(gridExtra)


sim_true_param_model_result_df = data.frame(data.table::fread("EDPM_simu_results/Results_Nimble_EDPM_Models_result.txt", sep = "\t"))

head(sim_true_param_model_result_df)
nrow(sim_true_param_model_result_df)


plot(sim_true_param_model_result_df$PIDE_AC_post_mean)

```


##  Plot number of outer clusters at each dataset

```{r}
# make a histogram plot for number of outer cluster used across replicated datasets
# draw vertical lines at mean and median
# only use white,black and gray colors

num_clusters <- sim_true_param_model_result_df$num_outer_clusters_used

# Calculate mean and median
mean_clusters <- mean(num_clusters, na.rm = TRUE)
median_clusters <- median(num_clusters, na.rm = TRUE)

# Create histogram
df_clusters <- data.frame(num_clusters = num_clusters)

p_clusters <- ggplot(df_clusters, aes(x = num_clusters)) +
  geom_histogram(aes(y = ..density..), bins = 30,
                 color = "black", fill = "gray80", alpha = 0.7) +
  geom_vline(aes(xintercept = mean_clusters, linetype = "Mean"),
             color = "black", size = 1) +
  geom_vline(aes(xintercept = median_clusters, linetype = "Median"),
             color = "gray40", size = 1) +
  scale_linetype_manual(name = "Statistics",
                        values = c("Mean" = "solid", "Median" = "dashed")) +
  labs(title = "True parametric DGM: EDPM fitted model (n =12000)",
       x = "Posterior mean of the number of outer clusters with allocation weight greater than 0.1", y = "Density") +
  theme_minimal(base_size = 12) +
  theme(legend.position = "bottom")

p_clusters

cat("Mean number of outer clusters:", round(mean_clusters, 2), "\n")
cat("Median number of outer clusters:", median_clusters, "\n")

```


### Plotting ALWAYS TREATED posterior means across 1000 replicated datasets

```{r}

posterior_means1 = sim_true_param_model_result_df$PIDE_AC_post_mean
df1 <- data.frame(posterior_means1)
p1 <- ggplot(df1, aes(x = posterior_means1)) +
  geom_histogram(aes(y = ..density..), bins = 30, 
                 color = "black", fill = "skyblue", alpha = 0.7) +
  geom_density(color = "red", size = 1) +
  labs(title = "Distribution of Posterior Means AT direct effects",
       x = "Posterior Means", y = "Density") +
  theme_minimal(base_size = 14)

p1


posterior_means2 = sim_true_param_model_result_df$PJIIE_AC_post_mean
df2 <- data.frame(posterior_means2)
p2 <- ggplot(df1, aes(x = posterior_means2)) +
  geom_histogram(aes(y = ..density..), bins = 30, 
                 color = "black", fill = "skyblue", alpha = 0.7) +
  geom_density(color = "red", size = 1) +
  labs(title = "Distribution of Posterior Means AT indirect effects",
       x = "Posterior Means", y = "Density") +
  theme_minimal(base_size = 14)

p2


posterior_means3 = sim_true_param_model_result_df$PCE_AC_post_mean
df3 <- data.frame(posterior_means3)
p3 <- ggplot(df1, aes(x = posterior_means3)) +
  geom_histogram(aes(y = ..density..), bins = 30, 
                 color = "black", fill = "skyblue", alpha = 0.7) +
  geom_density(color = "red", size = 1) +
  labs(title = "Distribution of Posterior Means AT total effects",
       x = "Posterior Means", y = "Density") +
  theme_minimal(base_size = 14)

p3


```


### Plotting VALUE ATTENTIVE posterior means across 1000 replicated datasets

```{r}

posterior_means1 = sim_true_param_model_result_df$PIDE_VA_post_mean
df1 <- data.frame(posterior_means1)
p1 <- ggplot(df1, aes(x = posterior_means1)) +
  geom_histogram(aes(y = ..density..), bins = 30, 
                 color = "black", fill = "skyblue", alpha = 0.7) +
  geom_density(color = "red", size = 1) +
  labs(title = "Distribution of Posterior Means VALUE ATTENTIVE direct effects",
       x = "Posterior Means", y = "Density") +
  theme_minimal(base_size = 14)

p1


posterior_means2 = sim_true_param_model_result_df$PJIIE_VA_post_mean
df2 <- data.frame(posterior_means2)
p2 <- ggplot(df1, aes(x = posterior_means2)) +
  geom_histogram(aes(y = ..density..), bins = 30, 
                 color = "black", fill = "skyblue", alpha = 0.7) +
  geom_density(color = "red", size = 1) +
  labs(title = "Distribution of Posterior Means VALUE ATTENTIVE indirect effects",
       x = "Posterior Means", y = "Density") +
  theme_minimal(base_size = 14)

p2


posterior_means3 = sim_true_param_model_result_df$PCE_VA_post_mean
df3 <- data.frame(posterior_means3)
p3 <- ggplot(df1, aes(x = posterior_means3)) +
  geom_histogram(aes(y = ..density..), bins = 30, 
                 color = "black", fill = "skyblue", alpha = 0.7) +
  geom_density(color = "red", size = 1) +
  labs(title = "Distribution of Posterior Means VALUE ATTENTIVE total effects",
       x = "Posterior Means", y = "Density") +
  theme_minimal(base_size = 14)

p3


```


### Plotting PRICE ATTENTIVE posterior means across 1000 replicated datasets

```{r}

posterior_means1 = sim_true_param_model_result_df$PIDE_PA_post_mean
df1 <- data.frame(posterior_means1)
p1 <- ggplot(df1, aes(x = posterior_means1)) +
  geom_histogram(aes(y = ..density..), bins = 30, 
                 color = "black", fill = "skyblue", alpha = 0.7) +
  geom_density(color = "red", size = 1) +
  labs(title = "Distribution of Posterior Means PRICE ATTENTIVE direct effects",
       x = "Posterior Means", y = "Density") +
  theme_minimal(base_size = 14)

p1


posterior_means2 = sim_true_param_model_result_df$PJIIE_PA_post_mean
df2 <- data.frame(posterior_means2)
p2 <- ggplot(df1, aes(x = posterior_means2)) +
  geom_histogram(aes(y = ..density..), bins = 30, 
                 color = "black", fill = "skyblue", alpha = 0.7) +
  geom_density(color = "red", size = 1) +
  labs(title = "Distribution of Posterior Means PRICE ATTENTIVE indirect effects",
       x = "Posterior Means", y = "Density") +
  theme_minimal(base_size = 14)

p2


posterior_means3 = sim_true_param_model_result_df$PCE_PA_post_mean
df3 <- data.frame(posterior_means3)
p3 <- ggplot(df1, aes(x = posterior_means3)) +
  geom_histogram(aes(y = ..density..), bins = 30, 
                 color = "black", fill = "skyblue", alpha = 0.7) +
  geom_density(color = "red", size = 1) +
  labs(title = "Distribution of Posterior Means PRICE ATTENTIVE total effects",
       x = "Posterior Means", y = "Density") +
  theme_minimal(base_size = 14)

p3


```


### Plotting NON-ACTIVE CUSTOMERS posterior means across 1000 replicated datasets

```{r}

posterior_means1 = sim_true_param_model_result_df$PIDE_NAC_post_mean
df1 <- data.frame(posterior_means1)
p1 <- ggplot(df1, aes(x = posterior_means1)) +
  geom_histogram(aes(y = ..density..), bins = 30, 
                 color = "black", fill = "skyblue", alpha = 0.7) +
  geom_density(color = "red", size = 1) +
  labs(title = "Distribution of Posterior Means NT direct effects",
       x = "Posterior Means", y = "Density") +
  theme_minimal(base_size = 14)

p1


posterior_means2 = sim_true_param_model_result_df$PJIIE_NAC_post_mean
df2 <- data.frame(posterior_means2)
p2 <- ggplot(df1, aes(x = posterior_means2)) +
  geom_histogram(aes(y = ..density..), bins = 30, 
                 color = "black", fill = "skyblue", alpha = 0.7) +
  geom_density(color = "red", size = 1) +
  labs(title = "Distribution of Posterior Means NT indirect effects",
       x = "Posterior Means", y = "Density") +
  theme_minimal(base_size = 14)

p2


posterior_means3 = sim_true_param_model_result_df$PCE_NAC_post_mean
df3 <- data.frame(posterior_means3)
p3 <- ggplot(df1, aes(x = posterior_means3)) +
  geom_histogram(aes(y = ..density..), bins = 30, 
                 color = "black", fill = "skyblue", alpha = 0.7) +
  geom_density(color = "red", size = 1) +
  labs(title = "Distribution of Posterior Means NT total effects",
       x = "Posterior Means", y = "Density") +
  theme_minimal(base_size = 14)

p3


```


## Compute bias, coverage and MSE

```{r}
calculate_statistics = function(results_df, true_value) {
  # Calculate Bias
  bias = as.numeric(results_df$posterior_mean) - true_value
  
  # Calculate Coverage (1 if true_value is within the CI, 0 otherwise)
  coverage = ifelse(as.numeric(results_df$lower_CI) <= true_value & as.numeric(results_df$upper_CI) >= true_value, 1, 0)
  
  # Calculate CI width (upper_CI - lower_CI)
  ci_width = as.numeric(results_df$upper_CI) - as.numeric(results_df$lower_CI)
  
  # Calculate MSE (Mean Squared Error)
  mse = (as.numeric(results_df$posterior_mean) - true_value)^2
  
  # Summarize Bias, Coverage, and MSE
  result = data.frame(
    bias = sprintf("%.5e", mean(bias)),
    coverage = mean(coverage),
    average_ci_width = mean(ci_width),
    mse = sprintf("%.5e", mean(mse))
  )
  
  return(result)
}


results_table_strata = function(PIDE_df_strata, PJIIE_df_strata, PCE_df_strata,
                                true_value_df, 
                                strata = c("active_customers", "value_attentive", "price_attentive", "non_active_customers")){
  result_df = calculate_statistics(PIDE_df_strata, true_value_df[strata,1])
  result_df = rbind( result_df, calculate_statistics(PJIIE_df_strata, true_value_df[strata,2]))
  result_df = rbind( result_df, calculate_statistics(PCE_df_strata, true_value_df[strata,3]))
  colnames(result_df) = c("BIAS",  "95% CI coverage rate", "Average CI width" ,"MSE")
  rownames(result_df) = c("IDE", "IIE", "TE")
  print(result_df)
}

active_customer_PIDE_result_df = data.frame(posterior_mean = sim_true_param_model_result_df$PIDE_AC_post_mean,
                                   lower_CI =  sim_true_param_model_result_df$PIDE_AC_lowerCI,
                                   upper_CI = sim_true_param_model_result_df$PIDE_AC_upperCI)


active_customer_PJIIE_result_df = data.frame(posterior_mean = sim_true_param_model_result_df$PJIIE_AC_post_mean,
                                   lower_CI =  sim_true_param_model_result_df$PJIIE_AC_lowerCI,
                                   upper_CI = sim_true_param_model_result_df$PJIIE_AC_upperCI)


active_customer_PCE_result_df = data.frame(posterior_mean = sim_true_param_model_result_df$PCE_AC_post_mean,
                                   lower_CI =  sim_true_param_model_result_df$PCE_AC_lowerCI,
                                   upper_CI = sim_true_param_model_result_df$PCE_AC_upperCI)


value_attentive_PIDE_result_df = data.frame(posterior_mean = sim_true_param_model_result_df$PIDE_VA_post_mean,
                                   lower_CI =  sim_true_param_model_result_df$PIDE_VA_lowerCI,
                                   upper_CI = sim_true_param_model_result_df$PIDE_VA_upperCI)


value_attentive_PJIIE_result_df = data.frame(posterior_mean = sim_true_param_model_result_df$PJIIE_VA_post_mean,
                                   lower_CI =  sim_true_param_model_result_df$PJIIE_VA_lowerCI,
                                   upper_CI = sim_true_param_model_result_df$PJIIE_VA_upperCI)


value_attentive_PCE_result_df = data.frame(posterior_mean = sim_true_param_model_result_df$PCE_VA_post_mean,
                                   lower_CI =  sim_true_param_model_result_df$PCE_VA_lowerCI,
                                   upper_CI = sim_true_param_model_result_df$PCE_VA_upperCI)


price_attentive_PIDE_result_df = data.frame(posterior_mean = sim_true_param_model_result_df$PIDE_PA_post_mean,
                                   lower_CI =  sim_true_param_model_result_df$PIDE_PA_lowerCI,
                                   upper_CI = sim_true_param_model_result_df$PIDE_PA_upperCI)


price_attentive_PJIIE_result_df = data.frame(posterior_mean = sim_true_param_model_result_df$PJIIE_PA_post_mean,
                                   lower_CI =  sim_true_param_model_result_df$PJIIE_PA_lowerCI,
                                   upper_CI = sim_true_param_model_result_df$PJIIE_PA_upperCI)


price_attentive_PCE_result_df = data.frame(posterior_mean = sim_true_param_model_result_df$PCE_PA_post_mean,
                                   lower_CI =  sim_true_param_model_result_df$PCE_PA_lowerCI,
                                   upper_CI = sim_true_param_model_result_df$PCE_PA_upperCI)


non_active_customer_PIDE_result_df = data.frame(posterior_mean = sim_true_param_model_result_df$PIDE_NAC_post_mean,
                                   lower_CI =  sim_true_param_model_result_df$PIDE_NAC_lowerCI,
                                   upper_CI = sim_true_param_model_result_df$PIDE_NAC_upperCI)


non_active_customer_PJIIE_result_df = data.frame(posterior_mean = sim_true_param_model_result_df$PJIIE_NAC_post_mean,
                                   lower_CI =  sim_true_param_model_result_df$PJIIE_NAC_lowerCI,
                                   upper_CI = sim_true_param_model_result_df$PJIIE_NAC_upperCI)


non_active_customer_PCE_result_df = data.frame(posterior_mean = sim_true_param_model_result_df$PCE_NAC_post_mean,
                                   lower_CI =  sim_true_param_model_result_df$PCE_NAC_lowerCI,
                                   upper_CI = sim_true_param_model_result_df$PCE_NAC_upperCI)


```


## Print Results 


### Active customer stratum

```{r}

results_table_strata(active_customer_PIDE_result_df , active_customer_PJIIE_result_df ,
                    active_customer_PCE_result_df ,
                    true_causal_estimands, "active_customer")


```


### Value attentive stratum

```{r}

results_table_strata(value_attentive_PIDE_result_df , value_attentive_PJIIE_result_df ,
                    value_attentive_PCE_result_df ,
                    true_causal_estimands, "value_attentive")


```


### Price attentive stratum

```{r}

results_table_strata(price_attentive_PIDE_result_df , price_attentive_PJIIE_result_df ,
                    price_attentive_PCE_result_df ,
                    true_causal_estimands, "price_attentive")


```


### Non-active customer stratum

```{r}

results_table_strata(non_active_customer_PIDE_result_df , non_active_customer_PJIIE_result_df ,
                    non_active_customer_PCE_result_df ,
                    true_causal_estimands, "non_active_customer")


```

